### 2016-02-12 chapters/abstract.tex
short notes for each section

Variability management is an essential part of working on product lines.
This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
To further simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line. This paper proposes a method for automatically generating feature models out of descriptive files and naming conventions.

>>>>

Variability management is an essential part of working on product lines.
As an established way to simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line. This paper proposes a method for automatically generating feature models out of descriptive files and naming conventions.
Furthermore existing methods of configuration are considered in this work and to develop an alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.

### 2016-02-12 chapters/background.tex
restructuring and changing for english style. starting to include a bibliography for references
slight restructuring
short notes for each section

Aktueller Stand der Technik, Beispiele, Vergleich der bestehenden Methoden, gemeinsame Schw\"achen finden

>>>>

\subsection{Feature Models}
Multi-purpose tool for product lines:
\begin{itemize}
\item Visualization of the possible features and their hierarchy
\item Classification of features and their dependencies (alternative/or; optional/mandatory/abstract)
\item Formal Representation of the whole product line $\Rightarrow$ computationally processable
\item assistance/foundation for configuration and variant validation
\end{itemize}

\subsection{Product configuration}
Customizing a product line to specific needs, resulting in a product/variant\\
Simplified to a list of (un-)selected features contained in the resulting product/variant\\

\subsection{Constraints, contradictions, SAT-solver}
Rules \& constraints specify (in-)valid configurations $\Rightarrow$ formalism of feature models allows SAT-solvers to check for validity\\
Already possible after each step of the ongoing configuration to check partial configurations

### 2016-02-12 chapters/concept.tex
short notes for each section

\subsection{Extraction of a feature model}
Describe the conventions and which rules are applied to generate a feature model out of it.

\subsection{Questionnaire Approach}
Use benefits of the existing approaches and overcome their shortcomings to solve the problem. State different variants and show the best one through comparison.

>>>>

\subsection{Extraction of a feature model}
The (Naming-)conventions and rules that are applied to generate a feature model out of it.\\
State the problems? Error-Handling on failure to comply the conventions?

\subsection{Questionnaire Approach}
Use questions to guide the user through a conditional configuration process. The questions, their order and the influences of the answers are pre-defined by a developer/an expert who uses his domain knowledge to design the questionnaire. Therefore, a data structure is introduced and mapped to a specific set of XML-tags.

### 2016-02-12 chapters/intro.tex
short notes for each section

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{V}{ariability} management is an essential part of working on product lines. There are several approaches trying to control the vast amount of product variants though configuration. This allows experts to apply their domain knowledge in order to a resulting product conforming to a users needs.

Feature Models are vital tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line. This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.

>>>>

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{S}{oftware} product lines. foo. There are several approaches trying to control the vast amount of product variants though configuration. This allows experts to apply their domain knowledge in order to a resulting product conforming to a users needs.

Feature Models are essential tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line. This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.
